\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-04-30 project-writings/paper.tex
Add pseudocode for the beta node insertion algorithm.

>>>>

\begin{figure}[ht]
\begin{center}
\begin{verbatim}
function addBetaNodesToFunc(cfg):
  for each b in cfg.basic-blocks():
    if b.numPredecessors() == 1 and isBranch(b.pred(0).lastInstruction())
      test = b.pred(0).lastInstruction()
      # find whether we are the true or false branch
      direction = (b == test.trueTarget())
      if test is of the form <x RELOP c>:
          r = computeRange(RELOP, c, direction)
          x' = b.insertFront(<Beta(x, r)>)
          replaceDominatedUses(x, x')

# Replace all uses of the instruction x that are dominated by
# the instruction x' with x'
function replaceDominatedUses(x, x'):
  for each use in x.uses():
    ins = use.instruction()
    if ins != x' and isDominatedUse(x', use):
      replaceUseWith(use, x')

function isDominatedUse(x', use):
  ins = use.instruction()
  if ins.isPhiNode():
    # Get the predecessor block that corresponds to the
    # argument of the phi node we are looking at
    phi-arg-pred-block = ins.block().pred(use.index())
    return blockDominates(x'.block(), phi-arg-pred-block)
  else:
    return blockDominates(x'.block(), x.block())
\end{verbatim}
\end{center}
\caption{Algorithm for inserting beta nodes}
\label{fig:add_betas}
\end{figure}
